\documentclass[a4paper]{MagicalCV}

\usepackage{xspace}
% Padding lists on the left
\usepackage{enumitem}
\setlist{labelindent=0pt, labelsep=2pt, leftmargin=6pt}
% Removing page numbers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

% Change the geometry
\geometry{left=1.2cm, top=.8cm, right=1.2cm, bottom=1.2cm, footskip=.5cm}

% Setting up Hyperlink
\hypersetup{%
  pdftitle={Curriculum Vitae},
  pdfauthor={Jean Simatic},
  pdfsubject={},
  pdfkeywords={}
}

% Defining your colors
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-purple}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

% start document
\begin{document}

% Last update time
\lastupdated

% Title name
\namesection{Jean}{Simatic}{
\email{\href{mailto:jean@simatic.org}{jean@simatic.org}}
\phone{+33 (0)6 28 13 12}
\github{\href{https://github.com/jsimatic}{jsimatic}}
\linkedin{\href{https://www.linkedin.com/in/jean-simatic/}{jean-simatic}}
\printinfo{\faGraduationCap}{\href{https://scholar.google.com/citations?user=57mWePYAAAAJ&hl=en&oi=ao}{scholar}}
\printinfo{\faGamepad}{\href{https://www.codingame.com/profile/914e5e6b4782c8b6dd1af4f35ef54c96249679}{CodingGame}}
}
% Column one
\begin{minipage}[t]{0.31\textwidth} 

% Education
\cvsection{Education} 

\subsection{Univ Grenoble Alpes}
\descript{PhD in circuit design/HLS}
\cvevent{2014 -- 2017}{Grenoble, FR}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
Design flow for ultra-low power: Non-uniform sampling and asynchronous circuits
\sectionsep

\subsection{ENSTA ParisTech}
\descript{Eng. Robotics and embedded systems}
\cvevent{2013 -- 2014}{Palaiseau, FR}
Multiprocessors on chip, embedded software, robotics, mecatronics
\sectionsep

\subsection{Univ. Pierre \& Marie Curie}
\descript{MSc. Electronic systems and Computer systems}
\cvevent{2013 -- 2014}{Paris, FR}
Mixed and analog circuit design, noise, design for test, MEMS
\sectionsep

\subsection{\'Ecole polytechnique}
\descript{Eng. Electrical Engineering}
\cvevent{2010 -- 2013}{Palaiseau, FR}
Digital circuit design, processor architecture, semi-conductors, optoelectronics,
network (Internet), statistics. French Robotics Cup.
\sectionsep

% Skills
\cvsection{Skills}

\newcommand\tb{\textbullet\xspace}

% TODO: \faCode{} 
\descript{\bf Development}
\begin{itemize}
\item Python \tb Pytest \tb Pandas \tb Conda
\item C/C++ \tb Rust \tb Make \tb Shell \tb Tcl
\item Git \tb Subversion \tb VS Code \tb Emacs
\item Docker \tb Vagrant \tb Kubernetes
\end{itemize}
\sectionsep

\descript{\bf \faSitemap{} Digital electronic}

\begin{itemize}
\item Vivado \tb Vitis HLS \tb Vitis \tb Quartus
\item SystemVerilog \tb Verilog \tb VHDL \tb SystemC \tb VHDL-AMS \tb Spice
\item DesignCompiler \tb PrimeTime \tb ModelSim \tb Innovus
\item I2C \tb SPI \tb AMBA \tb CAN
\end{itemize}
\sectionsep

\descript{\bf \faDesktop{} Software}

\begin{itemize}
\item Ubuntu \tb ArchLinux \tb CentOS \tb Win
\item OVH cloud \tb AWS \tb SSH \tb Nginx
\item Jira \tb Confluence \tb \LaTeX \tb MS Office
\end{itemize}
\sectionsep

\descript{\bf \faComments{} Languages}

\cvskill{French}{5}
\cvskill{English}{4.5}
\cvskill{Portuguese}{2}
\cvskill{German}{1}


% Column two
\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

% Experience
\cvsection{Work Experience}

\runsubsection{Deeptech Startup Chief Technology Officer} \\
\cvcompanyevent{HawAI.tech}{Feb 2019 -- Ongoing}{Grenoble, FR} 
\begin{tightemize}
\item Manage 10-person technical team (Scrum master then Product Owner).
\item Design of a modular architecture for low-power probabilistic circuits.
\item Implementation in software, FPGA (AWS F1) and ACAP (Xilinx Versal)
  using RTL and HLS. Develop test fixtures (Python) and host code (Python/C++).
\item Install and maintain the company's web services on cloud servers.
\end{tightemize}
\sectionsep

\runsubsection{Electronics R\&D Engineer \textbullet{} Stratup incubation} \\
\cvcompanyevent{Probayes}{Jan 2018 -- Feb 2019}{Grenoble, FR} 
\begin{tightemize}
\item Design highly efficient Bayesian sensor fusion and Bayesian filters
  using stochastic computing. Benchmark on Intel Cyclone V.
\item Lead legal, financial and business structuration for the spin-off
\end{tightemize}
\sectionsep

\runsubsection{Asynchronous Circuits PhD candidate} \\
\cvunivevent{TIMA Laboratory}{Nov 2014 -- Nov 2017}{Grenoble, FR} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Parse synchrounous FSM (from AUGH HLS) and generate asynchronous bundle data
  controllers using new synchronization protocol.
\item Design and test circuits for non-uniform sampling and filters. 
\end{tightemize}
\sectionsep

\runsubsection{Asynchronous Circuits Verification Intern} \\
\cvcompanyevent{Tiempo Secure}{April 2014 -- Oct 2014}{Saint-Martin d'Hères, FR} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Design of a verification tool for standard cells Verilog modules
\item Evaluation of a commercial fault simulator on QDI circuits
\end{tightemize}
\sectionsep

\runsubsection{Asynchronous Circuits Design Intern} \\
\cvuniveventnonboxed{Async Research Center}{April 2013 -- Aug 2013}{Porland, OR, USA} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Design of asynchronous IP for merge sort
\item Contribution to the development of a CAD tool (ARCWelder)
\end{tightemize}
\sectionsep


% Recent Projects
\cvsection{Recent Projects} 

\runsubsection{Test and generation of parametrized IP blocks} \\
\cvcompanyevent{HawAI.tech}{Aug 2022 – Feb 2023}{Grenoble, FR} 
Python set of utilities to handle in-house developped IP blocks.
Used Jinja templates to generate IP based on YAML config. Pytest fixtures
and parameterization to run parallelized regression tests.
\sectionsep

\runsubsection{Rust training} \\
\cvcompanyevent{Side-project}{Sep 2022 – Nov 2022}{Grenoble, FR} 
Learn Rust by the book, and solving puzzles. Small webscrapping and data plotting
project. Share leant concepts with a tutorial for HawAI.tech's team.
\sectionsep

\runsubsection{Bayesian grammar for an efficient OCR pipeline} \\
\cvcompanyevent{HawAI.tech}{June 2021 – Dec 2021}{Grenoble, FR} 
Integrate industrial client existing knowledge in Bayesian model (beam search
based) to correct errors of a PP OCR reader. Results post-processing and visualization
with pandas and matplotlib. Pipeline delivered in Docker.
\sectionsep

\runsubsection{FPGA Acceleration of Bayesian Matrix factorization} \\
\cvcompanyevent{HawAI.tech}{Nov 2020 – Oct 2021}{Grenoble, FR} 
Specify architecture in particular AXI and AXI-L interface with AWS F1 shell.
Develop AXI-Stream vector processing core. Co-develop Python API to generate
modularely handle each computation steps and manage the FPGA execution from a
Jupyter notebook. Demonstrated 5x speed/W on MovieLens.
\sectionsep

\end{minipage}
\end{document}